RProtoBuf: Efficient Cross-Language Data Serialization in R

### 2014-01-04 papers/rjournal/eddelbuettel-stokely.Rnw
renaming
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@701 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
table 1
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@702 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

%% TODO(de) Can we make this not break the width of the page?
\noindent
\begin{table}
\begin{tabular}{@{\hskip .01\textwidth}p{.40\textwidth}@{\hskip .015\textwidth}|@{\hskip .015\textwidth}p{0.55\textwidth}@{\hskip .01\textwidth}}
\hline
Schema : \texttt{addressbook.proto} & Example R Session\\
\hline
\begin{minipage}{.35\textwidth}
\vspace{2mm}
\begin{example}
package tutorial;
message Person {
 required string name = 1;
 required int32 id = 2;
 optional string email = 3;
 enum PhoneType {
   MOBILE = 0; HOME = 1;
   WORK = 2;
 }
 message PhoneNumber {
   required string number = 1;
   optional PhoneType type = 2;
 }
 repeated PhoneNumber phone = 4;
}
\end{example}
\vspace{2mm}
\end{minipage} & \begin{minipage}{.45\textwidth}
<<echo=TRUE>>=
library(RProtoBuf)
person <- new(tutorial.Person, id=1, name="Dirk")
person
person$name
person$name <- "Romain"
cat(as.character(person))
serialize(person, NULL)
@
\end{minipage} \\
\hline
\end{tabular}
\caption{The schema representation from a \texttt{.proto} file for the
  \texttt{tutorial.Person} class (left) and simple R code for creating
  an object of this class and accessing its fields (right).}
\label{tab:proto}
\end{table}

@@

The first versions of \CRANpkg{RProtoBuf} were written during 2009-2010,
with very significant contributions, both in code and design, made by
Romain Fran\c{c}ois. His continued influence on design and code is
appreciated. Several features of the package are influenced
by on the design of the \CRANpkg{rJava} package by Simon Urbanek
The user-defined table mechanism, implemented by Duncan Temple Lang for the
purpose of the \pkg{RObjectTables} package allowed the dynamic symbol lookup.
Kenton Varda was generous with his time in reviewing code and explaining
obscure protocol buffer semantics.  Karl Millar and Jeroen Ooms were
helpful in reviewing code or offering suggestions.  The contemporaneous
work by Saptarshi Guha on \pkg{RHIPE} was a strong initial motivator.

\bibliography{eddelbuettel-francois-stokely}

>>>>

%% TODO(de) Can we make this not break the width of the page?
\noindent
\begin{table}
\begin{tabular}{@{\hskip .01\textwidth}p{.40\textwidth}@{\hskip .02\textwidth}@{\hskip .02\textwidth}p{0.55\textwidth}@{\hskip .01\textwidth}}
\toprule
Schema : \texttt{addressbook.proto} & Example R Session\\
\cmidrule{1-2}
\begin{minipage}{.35\textwidth}
\vspace{2mm}
\begin{example}
package tutorial;
message Person {
 required string name = 1;
 required int32 id = 2;
 optional string email = 3;
 enum PhoneType {
   MOBILE = 0; HOME = 1;
   WORK = 2;
 }
 message PhoneNumber {
   required string number = 1;
   optional PhoneType type = 2;
 }
 repeated PhoneNumber phone = 4;
}
\end{example}
\vspace{2mm}
\end{minipage} & \begin{minipage}{.5\textwidth}
<<echo=TRUE>>=
library(RProtoBuf)
p <- new(tutorial.Person, id=1, name="Dirk")
class(p)
p$name
p$name <- "Murray"
cat(as.character(p))
serialize(p, NULL)
@
\end{minipage} \\
\bottomrule
\end{tabular}
\caption{The schema representation from a \texttt{.proto} file for the
  \texttt{tutorial.Person} class (left) and simple R code for creating
  an object of this class and accessing its fields (right).}
\label{tab:proto}
\end{table}

@@

The first versions of \CRANpkg{RProtoBuf} were written during 2009-2010,
with very significant contributions, both in code and design, made by
Romain Fran\c{c}ois. His continued influence on design and code is
appreciated. Several features of the package are influenced
by the design of the \CRANpkg{rJava} package by Simon Urbanek
The user-defined table mechanism, implemented by Duncan Temple Lang for the
purpose of the \pkg{RObjectTables} package allowed the dynamic symbol lookup.
Kenton Varda was generous with his time in reviewing code and explaining
obscure protocol buffer semantics.  Karl Millar and Jeroen Ooms were
helpful in reviewing code or offering suggestions.  The contemporaneous
work by Saptarshi Guha on \pkg{RHIPE} was a strong initial motivator.

\bibliography{eddelbuettel-stokely}
